High-level cognition is supported by information-rich but compressible brain activity patterns

### 2023-12-21 paper/main.tex
adding stats to Fig. 4 [WIP]

>>>>

These results make some intuitive sense. As the contextual information
available to participants increases (i.e., over time in the cognitively rich
``intact'' and ``paragraph'' conditions), it makes sense that this might
constrain neural responses to a greater extent. While this pattern may not
necessarily hold for \textit{every} possible story or stimulus, we suspect that
it is generally the case that our knowledge about what is happening in a story
tends to increase as we experience more about it. In turn, this could lead to
greater consistency in different people's interpretations of and neural
responses to the stimulus. Similarly, as participants are left to ``mind
wander,'' or as they experience mental fatigue (i.e., over time in the less
cognitively rich ``word'' and ``rest'' conditions), we suggest that this might
lead to greater variability in neural responses across people, resulting in
lower decoding accuracy. Again, it is not necessarily the case that every
possible ``unengaging'' stimulus will lead to greater neural variability as
time progresses, but we suspect this phenomenon is likely to hold for a variety
of such stimuli. These findings replicate at least to a limited extent (e.g.,
across both cognitively rich conditions and across both cognitively
impoverished conditions, and for the different groups of participants in each
of those conditions). However, determining whether these patterns generalize to
other stimuli would require additional study (with new stimuli).
